rotation_runs2019

### 2020-01-06 inst/documents/rotation_runs2019.Rmd
testing expts

nscenarios <- 20
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

@@

    #code to rerun approx this scenario, can be copied from pdf and pasted into R
    #has to cope with converting vectors to strings
    #spaces between args stop the pdf from messing with words
    cat(paste0( "run_rot(rot_interval=",linputs$rot_interval,", ", 
                "n_insecticides=",linputs$n_insecticides,", ",
                #"mort_or_freq='",linputs$mort_or_freq,"', ", #quotes dont work, freq is now default
                #'mort_or_freq="',linputs$mort_or_freq,'", ',
                "start_freqs=",signif(linputs$start_freqs,2),", ", 
                "cost=c(",paste(signif(linputs$cost,2),collapse=','),"), ", 
                "eff=c(",paste(signif(linputs$eff,2),collapse=','),"), ",               
                "dom_sel=c(",paste(signif(linputs$dom_sel,2),collapse=','),"), ",
                "dom_cos=c(",paste(signif(linputs$dom_cos,2),collapse=','),"), ",
                "rr=c(",paste(signif(linputs$rr,2),collapse=','),"), ",
                "expo_hi=",signif(linputs$expo_hi,2),", ",
                "male_expo_prop=",signif(linputs$male_expo_prop,2),", ",
                "coverage=",signif(linputs$coverage,2),", ",
                "migration=",signif(linputs$migration,2),", ",
                #"max_gen=",linputs$max_gen,", ", 
                "change_interval=",linputs$change_interval,
                #"min_rwr_interval=",linputs$min_rwr_interval,  
                ")\n\n") )

>>>>

nscenarios <- 200
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

@@

    #code to rerun approx this scenario, can be copied from pdf and pasted into R
    #has to cope with converting vectors to strings
    #spaces between args stop the pdf from messing with words
    cat(paste0( "run_rot(rot_interval=",linputs$rot_interval,", ", 
                "n_insecticides=",linputs$n_insecticides,", ",
                #"mort_or_freq='",linputs$mort_or_freq,"', ", #quotes dont work, freq is now default
                #'mort_or_freq="',linputs$mort_or_freq,'", ',
                "start_freqs=",signif(linputs$start_freqs,2),", ", 
                "cost=c(",paste(signif(linputs$cost,2),collapse=','),"), ", 
                "eff=c(",paste(signif(linputs$eff,2),collapse=','),"), ",               
                "dom_sel=c(",paste(signif(linputs$dom_sel,2),collapse=','),"), ",
                "dom_cos=c(",paste(signif(linputs$dom_cos,2),collapse=','),"), ",
                "rr=c(",paste(signif(linputs$rr,2),collapse=','),"), ",
                "expo_hi=",signif(linputs$expo_hi,2),", ",
                "male_expo_prop=",signif(linputs$male_expo_prop,2),", ",
                "coverage=",signif(linputs$coverage,2),", ",
                "migration=",signif(linputs$migration,2),", ",
                "max_gen=",linputs$max_gen,", ", 
                "change_interval=",linputs$change_interval,
                #"min_rwr_interval=",linputs$min_rwr_interval,  
                ")\n\n") )

### 2020-01-06 inst/documents/rotations_notes.Rmd
testing expts

>>>>

This B2 scenario 33 p34 is interesting, big benefit of rotations. One insecticide stays low in rotation seemingly due to use of others.

run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.013, cost=c(0.061,0.024,0.047), eff=c(0.97,0.88,0.72),
dom_sel=c(0.49,0.15,0.92), dom_cos=c(0.72,0.8,0.37), rr=c(0.25,0.51,0.42), expo_hi=0.52, male_expo_prop=0.92,
coverage=1, migration=0, max_gen=500, change_interval=10)
